Nitric-oxide-feedback to ciliary photoreceptor cells orchestrates UV avoidance in zooplankton

### 2022-05-27 text/Manuscript.Rmd
Add figure6
Add references

---
title: "Nitric-oxide-feedback to ciliary photoreceptor cells orchestrates UV avoidance in zooplankton"
author: "Kei Jokura, Nobuo Ueda, Martin Gühmann, Gáspár Jékely"
date: "*Living Systems Institute, University of Exeter, Stocker road, Exeter, EX4 4QD, UK*"
output:
  pdf_document: 
      latex_engine: xelatex
      template: style.tex
  html_document: 
    theme: lumen
geometry: left=0.8in,right=0.8in,top=0.8in,bottom=0.5in
mainfont: Arial
documentclass: article
classoption:
  - onecolumn
linestretch: 1.2
fontsize: 10pt
bibliography: references.bib
csl: elife.csl
---

@@

cPRCs expressing UV-absorbing c-opsin1 have high resting calcium levels and show hyperpolarising and subsequent depolarising responses to UV light (405 nm) (Verasztó et al., 2018). In the present study, we have shown that the cells that strongly synapse with cPRCs are interneurons that specifically express NOS (INNOS). The fluorescence intensity of DAF-FM, which specifically detected INNOS, showed a transient tonic-like increase dependent on UV stimulation of the cPRCs. The graph shows a decrease in intensity after UV light is switched off, but the response of DAF-FM to NO is irreversible and this decrease is due to breaching by the relatively strong excitation light. Attempts to measure changes in the intensity of the calcium indicator RGECO1a simultaneously with DAF-FM imaging did not lead to detection of changes in fluorescence intensity compared to GCaMP6s and could only visualise the cPRCs. In calcium imaging using GCaMP6s, INNOS identified by the positional relationship between the cPRC and INNOS and the labelling of RYa depolarised in clear synchrony with the hyperpolarising response of the cPRCs. This tonic response may involve dopaminergic nerves based on single-cell data (Fig) (Puopolo et al., 2001, Zhang et al., 2007, Randel et al., 2014). In the mammalian retina, it is known that signals from bipolar photoreceptor cells are transmitted to downstream NOS-expressing amacrine cells (NOAC), where NO is produced (Jacoby et al., 2018, Neuron). These suggest that UV stimulation of cPRCs causes the production of NO via a depolarising response of INNOS.

Our results suggest that NIT-GC1, which is specifically expressed in cPRCs, functions as a target for NO produced by INNOS and contributes to the regulation of the cPRC circuit transmission pathway via a depolarising response by increasing cGMP. In the mammalian retina, NO is an essential signalling molecule and one of the most well-studied (Cudeiro and Rivadulla, 1999). It has been reported that NO produced in one of the retinal cells modulates cGMP-mediated neurotransmission by activating presynaptic neural sGCs (general target of NO) through retrograde signalling (Vielma et al., 2014; Wei et al., 2012). In Platynereis cPRC, NIT-GC1 was also identified as having the property of producing cGMP in a NO-dependent manner. Furthermore, it is known that CNGAα, one of the cyclic nucleotide-gated channels, is specifically highly expressed in cPRC (Tosches et al., 2014), and in INNOS-cPRC signalling, NO is implicated in the neuromodulation of the cPRC by retrograde signalling. 
NO is a molecule with a very short half-life, and when functioning as a signalling molecule, NOS and sGC are known to localise very close together at synapses between neurons (Burette et al., 2002; Garthwaite., 2016). In our study, we found 12 sGCs in Platynereis, but none expressed in the cPRC. Localisation analysis of NOS and NIT-GC1 by antibody staining showed that the two proteins localised very close together in the anterior neurosecretory plexus region. Calcium imaging results using NOS mutant and NIT-GC1 knockdown larvae suggest that NIT-GC1 activation induces a depolarising response in the cPRC.

Another type of interneuron that strongly synapses with the cPRC is the INRGWa, which synapses directly onto the ciliomotor neuron and is therefore considered to be a very important neuron in the control of larval behaviour (Verasztó et al., 2018, Williams et al., 2018). The present results suggest that the depolarising response of the cPRC due to NO feedback induces INRGW activation. RGWamide is also a neuropeptide that induces larval downward swimming quite strongly (unpublished? need to show data?), and the delayed downward swimming of NOS mutant larvae in response to UV stimulation may be responsible for the failure of INRGW activation to occur. In addition, in many marine invertebrates, NO has been reported to be involved in many aspects of settlement behaviour and metamorphosis induction (1, 2, 3, 4, 5, 6, 7, 8, 9, 10). The downward swimming behaviour of Platynereis larvae is the first step in the onset of settlement behaviour and metamorphosis. These suggest that downward swimming due to NO activation of INRGWs may trigger the onset of settlement behaviour and metamorphosis (Conzelmann et al., 2013, Williams et al., 2015). These suggest that NO feedback signalling may act as a trigger for downward swimming via activation of INRGWs, which induces the initiation of settlement behaviour and metamorphosis.

An outstanding question is how the NO~NIT-GC response alters neuronal dynamics. NO is a single molecule and, due to its short half-life, cannot be transmitted over long distances and has a limited signalling repertoire. It has therefore been considered unsuitable for generating diversity in signalling compared to other signalling molecules such as neuropeptides and classical neurotransmitters (Jekely, 2021). However, our results in the present study indicate that NO-induced activation of NIT-GC1 is involved in the regulation of neuronal circuits (cPRC pathway). The NIT domain was originally found in bacteria and the existence of GCs with NIT domains was first reported by Moroz et al in 2020 (Shu et al., 2003; Moroz et al., 2020). It has been proposed that NIT domains in bacteria regulate cellular functions in response to changes in extracellular and intracellular nitrate and/or nitrite concentrations (Camargo et al., 2007). In fact, NO is a free radical molecule, with a half-life of 5 msec in vivo, and is readily converted to nitrate and nitrite (Santos et al., 2011; Garthwaite., 2016; Möller et al., 2019). And nitrate and nitrite have been reported to accumulate in cells and tissues with high NOS activity in placozoans and cnidarians (Moroz et al., 2004; Moroz et al., 2020). It is possible that the NIT domains of NIT-GC1 identified in this study may also be used for nitrate/nitrite sensing, as in bacteria. Furthermore, if they show different sensitivities to NO, nitrite and nitrate, it is possible that the temporal variation in their respective half-lives could give rise to a repertoire of activation timings (Lundberg  et al., 2011). In addition, we have found at least 15 NIT-GCs in the Platynereis transcriptome data, of which NIT-GC2 is highly expressed in the cPRC, in addition to NIT-GC1. Interestingly, NIT-GC2 showed a very different localisation pattern to NIT-GC1, and furthermore, the results of calcium imaging of cPRC in response to UV stimulation using NIT-GC2 knockdown larvae were the different dynamics (such that hyperpolarisation was suppressed) with NIT-GC1 knockdown. It was not clear from the present analysis whether this difference was due to differences in the localisation or the property of the NIT-GCs. However, the diversification and spatially different localisation patterns of NIT-GCs may increase their signalling repertoire. We also believe that the appearance of NIT-GCs was one of the means to generate the diversity of signalling pathways using NO during the early stages of nervous system evolution in metazoans, since sponges and ctenophores, where NO signalling is present, have no NIT-GCs at all, as many as 12 have been found in placozoans, and NIT-GCs are functional in the “proto-eye” circuit of Platynereis.

@@

Before designing the small guide RNA (sgRNA) for the sgRNA:Cas9 nuclease, splice sites and polymorphic sites in our laboratory culture were identified to avoid them. The sgRNA targeted the third exon of Platynereis dumerilii NOS (target site: 5'-GGGCAATACTGGCTCCACTC-3'). The sgRNA was assembled from two annealed oligonucleotides (5'-TAGGGCAATACTGGCTCCACTC-3', 5'-AAACGAGTGGAGCCAGTATTGC-3') forming overhangs for cloning into a BsaI site of the plasmid pDR27456 (Hwang et al. 2013)(42250, Addgene), which contains next to the BsaI site a tracrRNA sequence. The plasmid was then used to PCR amplify DNA (primers: T7, 5'-AAAAGCACCGACTCGGTGCC-3') for synthesizing the sgRNA. The DNA was purified with the QIAquick PCR Purification Kit (Qiagen). From the DNA, the sgRNA was synthesized with the MEGAshortscript Kit (Thermo Fisher Scientific) and was purified with the MEGAclear Kit (Thermo Fisher Scientific). Cas9-mRNA was transcribed, capped, and polyA-tailed with the mMessage mMachine Kit and the Poly(A) Tailing Kit (both Thermo Fisher Scientific) from a plasmid (pUC57-T7-RPP2-Cas9) containing the Cas9 ORF fused to 169 base pair 5' UTR from the Platynereis dumerilii 60S acidic ribosomal protein P2. The sgRNA (18 ng/ml) and the Cas9-mRNA (180 ng/µl) were coinjected into fertilized eggs of Platynereis dumerilii wild-type parents according to an established injection procedure (Conzelmann et al. 2013). The eggs were kept at 18°C for 45 min before injection and were injected at 14.5°C. The injected individuals were kept at 18°C for 5 to 8 days in 6-well- plates (Nunc multidish no. 150239, Thermo Scientific) and then cultured at 22°C until sexual maturity. The mature worms were crossed to wild-type worms and the progeny was genotyped, resulting in two founder lines, which were bred to homozygosity.

@@

Larvae were fixed and treated with Proteinase K, according to the conventional WMISH protocol (Tessmar-Raible et al., 2005), with fixation in 4% paraformaldehyde/ PTW (PBS with 0.05% Tween20) for 2 hr at room temperature, and Proteinase K treatment in 100 µg/ml Proteinase K/ PTW for 3 min (Tessmar-Raible et al., 2005). Specifically, for the HCR protocol, samples were processed in 1.5 ml tubes. Probe hybridization buffer, probe wash buffer, amplification buffer, and fluorescent HCR hairpins were purchased from Molecular Instruments (Los Angeles, USA). Hairpins associated with the b2 initiator sequence were labeled with Alexa Fluor 647, and the hairpins associated with the b3 initiator sequence were labeled with Alexa Fluor 546. To design probes for HCR, we used custom software (Kuehn et al., 2021) to create 20 DNA oligo probe pairs specific to P. dumerilii NOS, NIT-GC1, NIT-GC2, RYa-pNP (GenBank accession: JF811330.1), c-opsin1 (GenBank accession: AY692353.1), CNGAα (GenBank accession: KM199644.1), and MLD/pedal2-pNP (GenBank accession: KF515945.1). The NOS, NIT-GC1 and NIT-GC2 probes were designed to be associated with the b2 initiator sequence, while the RYa-pNP, c-opsin1, CNGAα and MLD/pedal2-pNP probes were designed to be associated with the b3 initiator sequence. For the detection stage, samples were pre-hybridized in 200 µl of probe hybridization buffer for 1 hr at 37°C, and then incubated in 250 µl hybridization buffer containing probe oligos (4 pmol/ml) overnight at 37°C. To remove excess probe, samples were washed 4× with 1 ml hybridization wash buffer for 15 min at 37°C, and subsequently 2× in 1 ml 5× SSCT (5× SSC with 0.1% Tween20) for 5 min at room temperature. For the amplification stage, samples were pre-incubated with 100 µl of amplification buffer for 30 min, room temperature, and then incubated with 150 µl amplification buffer containing fluorescently labeled hairpins (40nM concentration (2ul of 3uM stock in 150ul amplification buffer, snap-cooled as described; Choi et al., 2018) overnight in the dark at 25°C. To remove excess hairpins, samples were washed in 1 ml 5× SSCT at room temperature, twice for 5 min, twice for 30 min, and once for 5 min. During the first 30 min wash, samples were counterstained with DAPI (Cat. #40043, Biotium, USA).

@@

Whole-mount immunostaining of 2 day old Platynereis larvae fixed with 4% paraformaldehyde were carried out using primary antibodies raised against NIT-GC1, NIT-GC2, NOS, RYamide neuropeptide, RGWamide neuropeptide in rabbit, plus a commercial antibody raised against acetylated tubulin in mouse (Sigma T7451). The synthetic peptides contained an N-terminal Cys that was used for coupling during purification. Antibodies were affinity purified from sera as previously described (Conzelmann and Jékely 2012). Immunostainings were carried out as previously described (Conzelmann and Jékely 2012).

@@

Green cGull was used for the cGMP assay (Matsuda et al., 2017). A full-length Pdum-NIT-GC1 and -NIT-GC2 coding sequences were amplified by PCR starting from a Platynereis dumerilii cDNA library and cloned into the pcDNA3.1(+) vector using the T2A self-cleaving sequence. Cos-7 cells with low expression of endogenous soluble guanylate cyclase were used as cultured cells for gene expression. This cell line was purchased from Angio-proteomie (CAT no. cAP-0203). The Cos-7 cells were maintained at 37 °C in 35mm dishes (Nunc™ Glass Bottom Dishes) containing 3 mL of DMEM, high glucose glutamax medium (Thermo; Cat. No. 10566016) supplemented with 10% fetal bovine serum (Thermo; Cat. No. 10082147). Upon reaching confluency of approximately 85%, we transfected the cells with the plasmid containing Green cGull-T2A-NITGC1. Transfections were carried out with 150 ng of each plasmid and 0.3 μl of the transfection Lipofectamine 3000 Reagent (invitrogen; Cat. No. ???). Two days post-transfection, we removed the culture medium and substituted it for fresh DMEM-medium. For single-wavelength imaging experiments, cells in 35-mm dishes were washed twice and imaged in modified Ringer's buffer (140 mM NaCl, 3.5 mM KCl, 0.5mM NaH2PO4 , 0.5mM S-3 MgSO4 , 1.5 mM CaCl2 , 10 mM HEPES, 2 mM NaHCO3 and 5 mM glucose). Dishes were mounted on a stage heated at 37 °C and imaging was performed using an inverted microscope (LSM880, Zeiss) equipped with an oil-immersion objective lens (UApo/340, 40, NA = xx). Images were acquired using a xenon lamp, 460--495 nm excitation filter, 505-nm dichroic mirror and 510-- 550-nm emission filter (????). 8-br-cGMP and S-Nitroso-N-acetyl-D, L-penicillamine (SNAP) were purchased from Sigma-Aldrich (St. Louis, MO, USA) and Cayman Chemical (Ann Arbor, MI, USA). The exposure time of the EM-CCD camera was controlled by the ZEN software (Zeiss). Images were acquired every 15 s for 10 min and stimulation was initiated 2 min after starting image acquisition. Imaging data analysis was performed using ImageJ (National Institutes of Health, Bethesda, MD, USA).

>>>>

---
title: "Nitric-oxide-feedback to ciliary photoreceptor cells orchestrates UV avoidance in zooplankton"
author: "Kei Jokura, Nobuo Ueda, Martin Gühmann, Gáspár Jékely"
date: "*Living Systems Institute, University of Exeter, Stocker road, Exeter, EX4 4QD, UK*"
output:
  pdf_document: 
      latex_engine: xelatex
      template: "default"
  html_document: 
    theme: lumen
geometry: left=0.8in,right=0.8in,top=0.8in,bottom=0.5in
mainfont: Arial
documentclass: article
classoption:
  - onecolumn
linestretch: 1.2
fontsize: 10pt
bibliography: references.bib
csl: elife.csl
---

@@

cPRCs expressing UV-absorbing c-opsin1 have high resting calcium levels and show hyperpolarising and subsequent depolarising responses to UV light (405 nm) [@Verasztó2018]. In the present study, we have shown that the cells that strongly synapse with cPRCs are interneurons that specifically express NOS (INNOS). The fluorescence intensity of DAF-FM, which specifically detected INNOS, showed a transient tonic-like increase dependent on UV stimulation of the cPRCs. The graph shows a decrease in intensity after UV light is switched off, but the response of DAF-FM to NO is irreversible and this decrease is due to breaching by the relatively strong excitation light. Attempts to measure changes in the intensity of the calcium indicator RGECO1a simultaneously with DAF-FM imaging did not lead to detection of changes in fluorescence intensity compared to GCaMP6s and could only visualise the cPRCs. In calcium imaging using GCaMP6s, INNOS identified by the positional relationship between the cPRC and INNOS and the labelling of RYa depolarised in clear synchrony with the hyperpolarising response of the cPRCs. This tonic response may involve dopaminergic nerves based on single-cell data (Fig) [@puopolo2001][@zhang2007][@Randel2014a]. In the mammalian retina, it is known that signals from bipolar photoreceptor cells are transmitted to downstream NOS-expressing amacrine cells (NOAC), where NO is produced [@jacoby2018]. These suggest that UV stimulation of cPRCs causes the production of NO via a depolarising response of INNOS.

Our results suggest that NIT-GC1, which is specifically expressed in cPRCs, functions as a target for NO produced by INNOS and contributes to the regulation of the cPRC circuit transmission pathway via a depolarising response by increasing cGMP. In the mammalian retina, NO is an essential signalling molecule and one of the most well-studied [@Cudeiro1999]. It has been reported that NO produced in one of the retinal cells modulates cGMP-mediated neurotransmission by activating presynaptic neural sGCs (general target of NO) through retrograde signalling [@Vielma2014][@Wei2012]. In Platynereis cPRC, NIT-GC1 was also identified as having the property of producing cGMP in a NO-dependent manner. Furthermore, it is known that CNGAα, one of the cyclic nucleotide-gated channels, is specifically highly expressed in cPRC [@Tosches2014], and in INNOS-cPRC signalling, NO is implicated in the neuromodulation of the cPRC by retrograde signalling. NO is a molecule with a very short half-life, and when functioning as a signalling molecule, NOS and sGC are known to localise very close together at synapses between neurons [@burette2002][@garthwaite2015a]. In our study, we found 12 sGCs in Platynereis, but none expressed in the cPRC. Localisation analysis of NOS and NIT-GC1 by antibody staining showed that the two proteins localised very close together in the anterior neurosecretory plexus region. Calcium imaging results using NOS mutant and NIT-GC1 knockdown larvae suggest that NIT-GC1 activation induces a depolarising response in the cPRC.

Another type of interneuron that strongly synapses with the cPRC is the INRGWa, which synapses directly onto the ciliomotor neuron and is therefore considered to be a very important neuron in the control of larval behaviour [@Verasztó2018][@williams2017]. The present results suggest that the depolarising response of the cPRC due to NO feedback induces INRGW activation. RGWamide is also a neuropeptide that induces larval downward swimming quite strongly (unpublished? need to show data?), and the delayed downward swimming of NOS mutant larvae in response to UV stimulation may be responsible for the failure of INRGW activation to occur. In addition, in many marine invertebrates, NO has been reported to be involved in many aspects of settlement behaviour and metamorphosis induction [@leise2001; @bishop2003; @bishop2007; @pechenik2007; @castellano2014; @ueda2013; @ueda2014; @ueda2016; @yang2018; @zhu2020; @song2021]. The downward swimming behaviour of Platynereis larvae is the first step in the onset of settlement behaviour and metamorphosis. These suggest that downward swimming due to NO activation of INRGWs may trigger the onset of settlement behaviour and metamorphosis [@Conzelmann2013][@Williams2015]. These suggest that NO feedback signalling may act as a trigger for downward swimming via activation of INRGWs, which induces the initiation of settlement behaviour and metamorphosis.

An outstanding question is how the NO\~NIT-GC response alters neuronal dynamics. NO is a single molecule and, due to its short half-life, cannot be transmitted over long distances and has a limited signalling repertoire. It has therefore been considered unsuitable for generating diversity in signalling compared to other signalling molecules such as neuropeptides and classical neurotransmitters [@Jékely2021]. However, our results in the present study indicate that NO-induced activation of NIT-GC1 is involved in the regulation of neuronal circuits (cPRC pathway). The NIT domain was originally found in bacteria and the existence of GCs with NIT domains was first reported by Moroz et al in 2020 [@Shu2003; @Moroz2020]. It has been proposed that NIT domains in bacteria regulate cellular functions in response to changes in extracellular and intracellular nitrate and/or nitrite concentrations [@camargo2007]. In fact, NO is a free radical molecule, with a half-life of 5 msec in vivo, and is readily converted to nitrate and nitrite [@santos2011; @möller2019; @garthwaite2015a]. And nitrate and nitrite have been reported to accumulate in cells and tissues with high NOS activity in placozoans and cnidarians [@Moroz2004; @Moroz2020]. It is possible that the NIT domains of NIT-GC1 identified in this study may also be used for nitrate/nitrite sensing, as in bacteria. Furthermore, if they show different sensitivities to NO, nitrite and nitrate, it is possible that the temporal variation in their respective half-lives could give rise to a repertoire of activation timings [@lundberg2011]. In addition, we have found at least 15 NIT-GCs in the Platynereis transcriptome data, of which NIT-GC2 is highly expressed in the cPRC, in addition to NIT-GC1. Interestingly, NIT-GC2 showed a very different localisation pattern to NIT-GC1, and furthermore, the results of calcium imaging of cPRC in response to UV stimulation using NIT-GC2 knockdown larvae were the different dynamics (such that hyperpolarisation was suppressed) with NIT-GC1 knockdown. It was not clear from the present analysis whether this difference was due to differences in the localisation or the property of the NIT-GCs. However, the diversification and spatially different localisation patterns of NIT-GCs may increase their signalling repertoire. We also believe that the appearance of NIT-GCs was one of the means to generate the diversity of signalling pathways using NO during the early stages of nervous system evolution in metazoans, since sponges and ctenophores, where NO signalling is present, have no NIT-GCs at all, as many as 12 have been found in placozoans, and NIT-GCs are functional in the "proto-eye" circuit of Platynereis.

![Figure 6. Legend goes here](../figures/Figure6.png){width="100%"}

@@

Before designing the small guide RNA (sgRNA) for the sgRNA:Cas9 nuclease, splice sites and polymorphic sites in our laboratory culture were identified to avoid them. The sgRNA targeted the third exon of Platynereis dumerilii NOS (target site: 5'-GGGCAATACTGGCTCCACTC-3'). The sgRNA was assembled from two annealed oligonucleotides (5'-TAGGGCAATACTGGCTCCACTC-3', 5'-AAACGAGTGGAGCCAGTATTGC-3') forming overhangs for cloning into a BsaI site of the plasmid pDR27456 (Hwang et al. 2013)(42250, Addgene), which contains next to the BsaI site a tracrRNA sequence. The plasmid was then used to PCR amplify DNA (primers: T7, 5'-AAAAGCACCGACTCGGTGCC-3') for synthesizing the sgRNA. The DNA was purified with the QIAquick PCR Purification Kit (Qiagen). From the DNA, the sgRNA was synthesized with the MEGAshortscript Kit (Thermo Fisher Scientific) and was purified with the MEGAclear Kit (Thermo Fisher Scientific). Cas9-mRNA was transcribed, capped, and polyA-tailed with the mMessage mMachine Kit and the Poly(A) Tailing Kit (both Thermo Fisher Scientific) from a plasmid (pUC57-T7-RPP2-Cas9) containing the Cas9 ORF fused to 169 base pair 5' UTR from the Platynereis dumerilii 60S acidic ribosomal protein P2. The sgRNA (18 ng/ml) and the Cas9-mRNA (180 ng/µl) were coinjected into fertilized eggs of Platynereis dumerilii wild-type parents according to an established injection procedure [@Conzelmann2013a]. The eggs were kept at 18°C for 45 min before injection and were injected at 14.5°C. The injected individuals were kept at 18°C for 5 to 8 days in 6-well- plates (Nunc multidish no. 150239, Thermo Scientific) and then cultured at 22°C until sexual maturity. The mature worms were crossed to wild-type worms and the progeny was genotyped, resulting in two founder lines, which were bred to homozygosity.

@@

Larvae were fixed and treated with Proteinase K, according to the conventional WMISH protocol [@Tessmar-Raible2005], with fixation in 4% paraformaldehyde/ PTW (PBS with 0.05% Tween20) for 2 hr at room temperature, and Proteinase K treatment in 100 µg/ml Proteinase K/ PTW for 3 min [@Tessmar-Raible2005]. Specifically, for the HCR protocol, samples were processed in 1.5 ml tubes. Probe hybridization buffer, probe wash buffer, amplification buffer, and fluorescent HCR hairpins were purchased from Molecular Instruments (Los Angeles, USA). Hairpins associated with the b2 initiator sequence were labeled with Alexa Fluor 647, and the hairpins associated with the b3 initiator sequence were labeled with Alexa Fluor 546. To design probes for HCR, we used custom software [@Kuehn2022] to create 20 DNA oligo probe pairs specific to P. dumerilii NOS, NIT-GC1, NIT-GC2, RYa-pNP (GenBank accession: JF811330.1), c-opsin1 (GenBank accession: AY692353.1), CNGAα (GenBank accession: KM199644.1), and MLD/pedal2-pNP (GenBank accession: KF515945.1). The NOS, NIT-GC1 and NIT-GC2 probes were designed to be associated with the b2 initiator sequence, while the RYa-pNP, c-opsin1, CNGAα and MLD/pedal2-pNP probes were designed to be associated with the b3 initiator sequence. For the detection stage, samples were pre-hybridized in 200 µl of probe hybridization buffer for 1 hr at 37°C, and then incubated in 250 µl hybridization buffer containing probe oligos (4 pmol/ml) overnight at 37°C. To remove excess probe, samples were washed 4× with 1 ml hybridization wash buffer for 15 min at 37°C, and subsequently 2× in 1 ml 5× SSCT (5× SSC with 0.1% Tween20) for 5 min at room temperature. For the amplification stage, samples were pre-incubated with 100 µl of amplification buffer for 30 min, room temperature, and then incubated with 150 µl amplification buffer containing fluorescently labeled hairpins (40nM concentration (2ul of 3uM stock in 150ul amplification buffer, snap-cooled as described; [@Choi2018]) overnight in the dark at 25°C. To remove excess hairpins, samples were washed in 1 ml 5× SSCT at room temperature, twice for 5 min, twice for 30 min, and once for 5 min. During the first 30 min wash, samples were counterstained with DAPI (Cat. #40043, Biotium, USA).

@@

Whole-mount immunostaining of 2 day old Platynereis larvae fixed with 4% paraformaldehyde were carried out using primary antibodies raised against NIT-GC1, NIT-GC2, NOS, RYamide neuropeptide, RGWamide neuropeptide in rabbit, plus a commercial antibody raised against acetylated tubulin in mouse (Sigma T7451). The synthetic peptides contained an N-terminal Cys that was used for coupling during purification. Antibodies were affinity purified from sera as previously described [@Conzelmann2012]. Immunostainings were carried out as previously described [@Conzelmann2012].

@@

Green cGull was used for the cGMP assay [@Matsuda2017]. A full-length Pdum-NIT-GC1 and -NIT-GC2 coding sequences were amplified by PCR starting from a Platynereis dumerilii cDNA library and cloned into the pcDNA3.1(+) vector using the T2A self-cleaving sequence. Cos-7 cells with low expression of endogenous soluble guanylate cyclase were used as cultured cells for gene expression. This cell line was purchased from Angio-proteomie (CAT no. cAP-0203). The Cos-7 cells were maintained at 37 °C in 35mm dishes (Nunc™ Glass Bottom Dishes) containing 3 mL of DMEM, high glucose glutamax medium (Thermo; Cat. No. 10566016) supplemented with 10% fetal bovine serum (Thermo; Cat. No. 10082147). Upon reaching confluency of approximately 85%, we transfected the cells with the plasmid containing Green cGull-T2A-NITGC1. Transfections were carried out with 150 ng of each plasmid and 0.3 μl of the transfection Lipofectamine 3000 Reagent (invitrogen; Cat. No. ???). Two days post-transfection, we removed the culture medium and substituted it for fresh DMEM-medium. For single-wavelength imaging experiments, cells in 35-mm dishes were washed twice and imaged in modified Ringer's buffer (140 mM NaCl, 3.5 mM KCl, 0.5mM NaH2PO4 , 0.5mM S-3 MgSO4 , 1.5 mM CaCl2 , 10 mM HEPES, 2 mM NaHCO3 and 5 mM glucose). Dishes were mounted on a stage heated at 37 °C and imaging was performed using an inverted microscope (LSM880, Zeiss) equipped with an oil-immersion objective lens (UApo/340, 40, NA = xx). Images were acquired using a xenon lamp, 460--495 nm excitation filter, 505-nm dichroic mirror and 510-- 550-nm emission filter (????). 8-br-cGMP and S-Nitroso-N-acetyl-D, L-penicillamine (SNAP) were purchased from Sigma-Aldrich (St. Louis, MO, USA) and Cayman Chemical (Ann Arbor, MI, USA). The exposure time of the EM-CCD camera was controlled by the ZEN software (Zeiss). Images were acquired every 15 s for 10 min and stimulation was initiated 2 min after starting image acquisition. Imaging data analysis was performed using ImageJ (National Institutes of Health, Bethesda, MD, USA).
